Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-05-18 analysis/paper/paper.Rmd
work on table of counts

---
title: "Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan"
author:
  - Li-Ying Wang
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

1. Overall summary of  Raw material, shape/type and counts of ornaments
There are `r sample_size` ornaments excavated from the 40 sampling squares, which accounts for `r sample_pro`% of the total number of ornaments found in the excavation section where they were from. Figure \@ref(fig:plot-all-ornaments-count) shows that the most common ornament is golden bead with the number of 143, followed by 121 glass beads, 46 agate beads, 35 metal rings, and 22 metal bells. Ornaments in some categories are divided into sub-types due to the variations of shape, such as agate bead, metal ring, and metal bell. Table ? shows the subtypes for the major ornaments.

@@

```{r tab-all}
ornaments_shape <-
  ornaments_period %>% 
  ungroup() %>% 
  select(Categories, Type) %>% 
  distinct(Categories, Type, .keep_all = TRUE) %>% 
  filter(Categories != c("Unknown Metal", "Bone Ornament"))

@@

>>>>

---
title: "Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan"
author:
  - Li-Ying Wang
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

1. Overall summary of  Raw material, shape/type and counts of ornaments
There are `r sample_size` ornaments excavated from the 40 sampling squares, which accounts for `r sample_pro`% of the total number of ornaments found in the excavation section where they were from. Figure \@ref(fig:plot-all-ornaments-count) shows that the most common ornament is golden bead with the number of 143, followed by 121 glass beads, 46 agate beads, 35 metal rings, and 22 metal bells. Ornaments in some categories are divided into sub-types due to the variations of shape, such as agate bead, metal ring, and metal bell. Table \@ref(tab:tab-all) shows the subtypes for the major ornaments.

@@

```{r taball}
# clean some 
ornaments_period_clean <- 
ornaments_period %>% 
  mutate(Type = str_remove(Type, "prism/"),
         Type = ifelse(Type == "glass bead", "medium bead", Type))

ornaments_shape <-
  ornaments_period_clean %>% 
  group_by(period, Categories, Type ) %>% 
  tally() %>% 
  spread(period, n, fill = 0) %>% 
  filter(!Categories %in% c("Unknown Metal",

                            "Perforated plate", 
                            "Knited item",
                            "Hair pin",
                            "Bone Ornament",
                            "Metal Piece",
                            "Glass ring"))

@@

Table \@ref(tab:taball) shows the subtypes for the major ornaments.
